Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-12 paper/structureScene.tex
Edit conclusion

Representing a scene using a reduced set of representatives, with adapted similarity strategies, allows us to improve ASSR performance compared to the BOF approaches based on GMMs which have been demonstrated to be equivalent to early integrations scheme on well-balanced datasets \cite{lagrange:hal-01082501}. These results advocate for a hierarchical model of the scene, where short-time structure -- \ie below a second -- is represented using a convolutional network such as the scattering transform, whereas larger time scales -- \ie over a second -- are modeled as adaptive aggregates.

Within a supervised setting of acoustic scene classification (ASC), we have shown the comparative benefits of log-scattering features over MFCCs, of majority voting at a mid-level time scale of $T=372\,\mathrm{ms}$ over prediction at a high-level time scale of $T=24\,\mathrm{s}$, and of an adapted Gaussian kernel over the linear kernel in support vector machine classification.
%, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}

Those outcomes shall be studied further in future work by considering larger databases and more diverse applications, such as pleasantness prediction \cite{lafaySoundscapePilot} as well as emerging tasks in ecoacoustics.

>>>>

Representing a scene using a reduced set of representatives, with adapted similarity strategies, allows us to improve ASSR performance compared to the early-integration scheme which have been demonstrated to be equivalent to BOF approaches using GMMs on well-balanced datasets \cite{lagrange:hal-01082501}. These results advocate for a hierarchical model of the scene, where short-time structure--\ie below a second--is represented using a convolutional network such as the scattering transform, whereas larger time scales--\ie over a second--are modeled as adaptive aggregates.

Within a supervised setting of acoustic scene classification (ASC), we have shown the comparative benefits of log-scattering features over MFCCs, of majority voting at a mid-level time scale of $T=372\,\mathrm{ms}$ over prediction at a high-level time scale of $T=24\,\mathrm{s}$, and of an adapted Gaussian kernel over the linear kernel in support vector machine classification for the tasks we considered.
%, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}

These outcomes shall be studied further in future work by considering larger databases and more diverse applications, such as pleasantness prediction \cite{lafaySoundscapePilot} as well as other emerging tasks in ecoacoustics.
